\Title

### 2021-05-10 latex/paper/main.tex
Modified the monte carlo description
Wrote the first draft of the hardware description

%/========== Experiments ==========/%
\section{Simulation Results}\label{sec:simulations}
In Section \ref{sec:experiments} we will test our VNHC on the physical acrobot
built by Xingbo Wang \cite{xingbo_thesis} (Figure \ref{fig:xingbo-acrobot}).
To compare apples to apples, we will simulate our VNHC using the parameters of
the physical system (Table \ref{tab:acrobot-parameters}).

@@

@@

Note that these parameters do not correspond to our simplified acrobot in Figure
\ref{fig:simple-acrobot-model}, but rather to the more general acrobot model in
Figure \ref{fig:acrobot-model}.
In particular, the inertia matrix and potential function are \textbf{not}
described by ~\eqref{eqn:acrobot-inertia}-\eqref{eqn:acrobot-potential}.
The correct \(M(q)\) and \(V(q)\) can be found in Wang's thesis
\cite{xingbo_thesis}.
\textbf{TODO: put them here if there is space}.
If our VNHC injects energy into this acrobot, then we can infer that
VNHCs are robust to model mismatch.

@@

To verify numerically that the acrobot would consistently achieve rotations, we
ran a Monte-Carlo simulation \cite{montecarlo} where we initialized the acrobot
randomly inside the sublevel set
\[
    \left\{(q_u,p_u) \in \SxR \mid
    E(q_u,p_u) \leq E\left(\frac{\pi}{32},0\right)\right\}
    ,
\] 
and measured how long it took to begin rotating.
The results in Figure \ref{fig:acrobot-mc} show that
the acrobot always rotated within 10--35 seconds.

@@

@@

\subsection{Hardware Description}
\textbf{TODO: paraphrase xingbo. 2 arduinos, 3d printed, battery in leg,
parameters of system, etc}

@@

\textbf{TODO: rework this section. In simulation we showed that we gain energy
everywhere. Here we only gain energy up to speed 0.195 because of friction.}
Wang's acrobot has an encoder which measures \(q_u\) and
\(\dot{q}_u\).
Additionally, the leg actuator is a servo motor with a built-in PID controller
which provides measurements of \(q_a\).
To implement our VNHC, we estimated \(\dot{q}_a\) through sequential values of
\(q_a\) and computed \(p_u\) through \(p_u = e_1^T M(q) \dot{q}\).
We directly assigned the actuator setpoint at iteration \(k \in \mathbb{Z}_{> 0}\)
via \(q_a^{k} = \arctan(10 p_u^{k-1})\).
We then performed the following tests.

>>>>

%/========== Experiments ==========/%
\section{Simulation Results}\label{sec:simulations}
In Section \ref{sec:experiments} we will test our VNHC on the physical acrobot
built by Xingbo Wang \cite{xingbo_thesis}.

Note that this acrobt does not correspond to the simple acrobot in Figure
\ref{fig:simple-acrobot-model}, but rather to the more general acrobot model in
Figure \ref{fig:acrobot-model}.
If we define 
\begin{align*}
    m_{11}(q) := &m_a l_u^2 + 2m_al_ul_{c_a}\cos(q_a) + m_al_{c_a}^2 +
    m_ul_{c_u}^2 \\
                 &+ J_u + J_a
                 , \\
    m_{12}(q) := &m_al_{c_a}^2 + m_al_ul_{c_a}\cos(q_a) + J_a
    , \\
    m_{22}(q) := &m_al_{c_a}^2 + J_a,
\end{align*}
then the inertia matrix and potential for the physical acrobot are
\begin{align*}
    M(q) &= \begin{bmatrix}
        m_{11}(q) & m_{12}(q) \\
        m_{12}(q) & m_{22}(q)
    \end{bmatrix}
    , \\
    V(q) &= g\big(m_al_{c_a}(1-c_{ua})
    + (m_al_u + m_ul_{c_u})(1-c_u)\big).
\end{align*}

@@

We will simulate our VNHC using the parameters of
this physical robot, which can be found in Table \ref{tab:acrobot-parameters}.
If our VNHC injects energy into this acrobot, then we can infer that
VNHCs are robust to model mismatch.

@@

@@

To verify numerically that the acrobot would consistently achieve rotations, we
ran a Monte-Carlo simulation \cite{montecarlo} where we initialized the acrobot
randomly inside the sublevel set
\[
    \left\{(q_u,p_u) \in \SxR \mid
    E(q_u,p_u) \leq E\left(\frac{\pi}{32},0\right)\right\}
    ,
\] 
and measured how long it took to begin rotating.
The results in Figure \ref{fig:acrobot-mc} show that
the acrobot always rotated within 20--40 seconds.

@@

\subsection{Hardware Description}
In this section we will demonstrate that our VNHC is robust to friction, sensor
noise, and other real-world considerations by testing it on the physical
acrobot built by Xingbo Wang \cite{xingbo_thesis} 
(Figure \ref{fig:xingbo-acrobot}.

@@

This acrobot is comprised of two 3D-printed links: a torso and a leg.
The torso link houses an Arduino Nano microcontroller unit (MCU) which controls
a Dynamixel RX24F servo motor between the torso and the leg.
The MCU and the motor are powered by a 12V battery held in a compartment
in the leg.

The torso is rigidly attached to a metal bar, which is held up by two wooden
posts.
On the exterior of one post is a control box with a power switch and a second
Arduino Nano 328.
The purpose of this control box is to read measurements from a rotary
encoder connected to the metal bar, and to transmit these measurements to the
MCU.
The two Arduinos communicate through wires attached to a slip ring on the metal
bar, and the signals are transmitted via I2C.
The control box also provides a USB interface which allows the user to read the
data from the acrobot in real time.

VNHC implementation requires full knowledge of the acrobot's phase. 
The rotary encoder directly measures \(q_u\), and the Dynamixel servo
motor provides measurements of \(q_a\).
However, there are no sensors measuring the velocity \(\dot{q}\), which means we cannot
directly evaluate \(p_u\) and \(p_a\).
To resolve this issue, the MCU estimates \(\dot{q}\) using sequential measurements of \(q\)
and a washout filter.
We then compute \(p = M(q)\dot{q}\) for use in the VNHC controller.

Communication between the Arduinos restricts the sampling rate of \(p\) to
500Hz.
This low sampling rate results in a noisy momentum signal, which suffers
from noticeable phase lag.
This also rate-limits the control signal to \(500\)Hz, which impacts any control
implementation.

Finally, The Dynamixel servo motor does not have a torque control mode; instead,
we can assign the servo setpoint at iteration \(k \in \mathbb{Z}_{> 0}\)
via \(q_a^{k} = \arctan(10 p_u^{k-1})\).
Unfortunately, this negatively affects the stabilization to the constraint
manifold because we are introducing timing errors from the servo's built-in PID
controller.

The system was given the name SUGAR: Simple Underactuated Gymnastics and
Acrobatics Robot.
Its dynamic parameters are outlined in Table \ref{tab:acrobot-parameters}.

@@

\textbf{TODO: rework this section. In simulation we showed that we gain energy
everywhere. Here we only gain energy up to speed 0.195 because of friction.}
We performed the following tests.
